%	Section Title

\cvsection{Experience}

%	Content
\begin{cventries}

  \cventry
    {Co-Founder (Node • AWS)}
    {\href{https://dendron.so}{Dendron - Hierarchical note taking tool}}
    {Seattle}
    {February 2021 - Current}
     {
      \begin{cvitems}
        \item {Building the best note taking tool.}
      \end{cvitems}
    }

  \cventry
    {Software engineer (React • Python • Django • Postgres • Flutter)}
    {\href{https://codeyellow.nl}{CodeYellow - Software Consultancy}}
    {Eindhoven}
    {August 2020 - February 2021}
     {
      \begin{cvitems}
        \item {Building web \& native Flutter apps for transportation and factory management.}
      \end{cvitems}
    }

  \cventry
    {Software engineer (Go • React Native • Postgres)}
    {\href{https://www.rekki.com}{Rekki - Ordering app for chefs and suppliers}}
    {London}
    {January 2020 - March 2020}
     {
      \begin{cvitems}
        \item {Made many React Native components and wrote microservices in Go.}
      \end{cvitems}
    }

  \cventry
    {Software engineer (TS • React • Python • GraphQL • Postgres)}
    {\href{https://www.gyana.com}{Gyana - No-Code Data Science}}
    {London}
    {June 2019 - October 2019}
     {
      \begin{cvitems}
        \item {Made tools to visualize geospatial data (> 50TB), markdown editor, exporter utility.}
      \end{cvitems}
    }

  \cventry
    {Software engineer (TS • React • Redux • Node • Kubernetes • Postgres)}
    {\href{https://www.enpicom.com}{Enpicom - Immunotherapy analysis}}
    {Den Bosch}
    {January 2019 - April 2019}
     {
      \begin{cvitems}
        \item {Wrote analysis \& data processing algorithms in Python with visualizations in D3.js.}
      \end{cvitems}
    }

  \cventry
    {Software engineer (TS • React • Redux • Node • Postgres)}
    {\href{https://www.deedmob.com}{Deedmob - Volunteering}}
    {Amsterdam}
    {July 2018 - December 2018}
     {
      \begin{cvitems}
        \item {Migrated code from JS to TS. Did company on-boarding, white label product.}
      \end{cvitems}
    }

  \cventry
    {Co-Founder (Go • TS • NextJS • Postgres • Prisma)}
    {\href{https://learn-anything.xyz}{Learn Anything - Learn \& Share Ideas}}
    {}
    {May 2017 - Current}
     {
      \begin{cvitems}
        \item {Leading project with design/code/management. 12,000+ \href{https://github.com/learn-anything/learn-anything}{GitHub} stars.}
      \end{cvitems}
    }

\end{cventries}
