% Section Title
\cvsection{Open Source Projects}

% Content
\begin{cventries}

  \cventry
    {DSL to easily modify \href{https://github.com/tekezo/Karabiner-Elements}{Karabiner} configuration. Written in ruby.}
    {\href{https://github.com/nikitavoloboev/karabiner-generator\#readme}{Karabiner generator}}
    {}
    {2018}
    {
    }

  \cventry
    {Alfred workflow to search through all topics found in Learn Anything website. Written in Go.}
    {\href{https://github.com/nikitavoloboev/alfred-learn-anything\#readme}{Alfred Learn Anything}}
    {}
    {2018}
    {
    }

    \cventry
    {Alfred workflow to search through any website on the web. Written in Go.}
    {\href{https://github.com/nikitavoloboev/alfred-web-searches\#readme}{Alfred Web Searches}}
    {}
    {2017}
    {
    }

    \cventry
    {Curated list of macOS applications and my personal configuration with using macOS.}
    {\href{https://github.com/nikitavoloboev/my-mac-os\#readme}{My macOS}}
    {}
    {2017}
    {
    }

    \cventry
    {Personal wiki where I share everything I know as an online book.}
    {\href{https://wiki.nikitavoloboev.xyz\#readme}{Knowledge Wiki}}
    {}
    {2017}
    {
    }

    \cventry
    {Alfred workflow to search through all the awesome GitHub curated lists. Written in Go.}
    {\href{https://github.com/nikitavoloboev/alfred-awesome-lists\#readme}{Alfred Awesome Lists}}
    {}
    {2017}
    {
    }

    \cventry
    {Command line tool to create LICENSE files quickly. Written in Go.}
    {\href{https://github.com/nikitavoloboev/license-up\#readme}{License Up}}
    {}
    {2017}
    {
    }

    \cventry
    {Go library to parse markdown files to grab various things.}
    {\href{https://github.com/nikitavoloboev/markdown-parser\#readme}{Markdown parser}}
    {}
    {2017}
    {
    }

    \cventry
    {Alfred workflow to create various Web Submissions. Written in Go.}
    {\href{https://github.com/nikitavoloboev/alfred-ask-create-share\#readme}{Alfred Ask Create Share}}
    {}
    {2017}
    {
    }

\end{cventries}
